Trending assessment for nowcasts, measurements, and forecasts

### 2024-03-08 sections/01-introduction.tex
Update on Overleaf.

As outlined above, trending evaluation is crucial for measurements, predictions, and forecasts. 
However, regardless of the application domain, most conventional method comparisons and evaluations consider local absolute differences in different ways without directly assessing whether the correct direction of change is output.

>>>>

As outlined above, trending evaluation is crucial for measurements, predictions, and forecasts. 
However, regardless of the area of application, most conventional method comparisons and assessments consider local absolute differences in different ways without directly assessing whether the correct direction of change is being predicted or measured.In this paper, we want to complement the current evaluation measures with trending measurements and propose the evaluation methods that assess the trendability of a method.
